Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-12-18 aa workingdraft/draft.tex

In our study, we focused specifically on capture efficiency of emergent stems. Capture efficiency is a geometrical parameter that describes the ability of a collector, usually modeled as a cylinder for vegetation stems, to capture suspended sediment particles in an open-channel flow (Figure \ref{fig:capeff}). It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width containing all particles that contact a single collector ($w_u$) and the collector's diameter ($d_c$). Effective capture efficiency ($\eta^\prime=p_r\eta$; ECE) accounts for the fact that not all particles coming into infinitessimally close proximity to a collector will adhere to it \cite{spielman1977particle}, and that affixed particles may later be sheared off \cite{defina2010floating}, thus including probability of retention ($p_r$) as a multiplicand in its calculation. ECE is the appropriate variable for the empirical estimates made by our study and presumably in any other settings that involve $p_r$ as an implicit factor.

@@

TKE was consistently found to increase with increasing flow velocity as expected (Table \ref{tbl:turbulence}). Generally, higher collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the lower and middle collector-density treatments. A slight decrease actually occurred thereafter (between the middle and highest collector densities) for the middle and highest $\Rey_c$ treatments, with a slight increase for the lowest $\Rey_c$ treatment. The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the middle treatment's $\phi_c$ value.

@@

@@

Aside from the outlier at the mid $\Rey_c$, lowest collector-density treatment, all of our observations were in agreement with the power-law model from Fauria et al. \cite{Fauria_2015} (Figure \ref{fig:compplot}). In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE). Moreover, the model relating $C$ to $\phi_c$ yielded relatively good fit (R$^2$ = 0.82):

@@

\noindent It underestimated $C$ for all of our collector-density treatments, and overestimated it for both of those from Fauria et al. ($\phi_c$ = 0.82\%, 2.16\%), but by a relatively small magnitude in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).

>>>>

In our study, we focused specifically on capture efficiency of emergent stems, one of the less well-studied effects of vegetation. Capture efficiency is a geometrical parameter that describes the ability of a collector, usually modeled as a cylinder for vegetation stems, to capture suspended sediment particles in an open-channel flow (Figure \ref{fig:capeff}). It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width containing all particles that contact a single collector ($w_u$) and the collector's diameter ($d_c$). Effective capture efficiency ($\eta^\prime=p_r\eta$; ECE) accounts for the fact that not all particles coming into infinitessimally close proximity to a collector will adhere to it \cite{spielman1977particle}, and that affixed particles may later be sheared off \cite{defina2010floating}, thus including probability of retention ($p_r$) as a multiplicand in its calculation. ECE is the appropriate variable for the empirical estimates made by our study and presumably in any other settings that involve $p_r$ as an implicit factor.

@@

TKE was consistently found to increase with increasing flow velocity as expected (Table \ref{tbl:turbulence}). Generally, higher collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the lower and middle collector-density treatments. A slight decrease actually occurred thereafter (between the middle and highest collector densities) for the middle and highest $\Rey_c$ treatments, with a slight increase for the lowest $\Rey_c$ treatment. The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the middle treatment's $\phi_c$ value. ECE and TKE exhibited a negative relationship across the experimental parameter space (n = 9) taken as a whole (Figure \ref{fig:tke}).

@@

\begin{figure}[H]
\centering
\includegraphics[width=5in]{../pics/tke.png}
\caption{Effective capture efficiency as a function of turbulent kinetic energy for all experimental treatments studied.}
\label{fig:tke}
\end{figure}

@@

Aside from the outlier at the mid $\Rey_c$, lowest collector-density treatment, all of our observations were in agreement with the power-law model from Fauria et al. \cite{Fauria_2015} (Figure \ref{fig:compplot}). In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE). Moreover, the model relating $C$ to $\phi_c$ yielded marginally good fit (R$^2$ = 0.82):

@@

\noindent It underestimated $C$ for all of our collector-density treatments, and overestimated it for both of those from Fauria et al. ($\phi_c$ = 0.82\%, 2.16\%), but by a relatively small magnitude in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5). Data scarcity should be considered a limiting factor in the interpretation of these results.
